### 2016-03-05 Projects/DelCo_2014_2015/Reports/Hose_Stream_Report/TeX_Files/DelCo_Hose_Stream_Tests.tex
Combined Test_17b exp file with Test_17, updated hose plot script/report

Fig.~\ref{fig:Test_16_BDP_A10_Avg_All} contains a plot of the average measured velocity through the interior stairwell door (A10) for the straight, narrow fog, and wide fog stream patterns during Test 16. Similar plots of the average measured velocity through the interior doorway for Tests 17, 33, and 70 are presented in Appendix~\ref{sec:monitor_figs}.

@@

Fig.~\ref{fig:Test_18_BDP_A10_Avg_All} contains a plot of the average measured velocity through the interior stairwell door (A10) for the straight, narrow fog, and wide fog stream patterns being applied in a fixed position, a sweeping pattern, a clockwise rotation, and counter clockwise rotation during Test 18. Similar plots of the average measured velocity through the interior doorway for Tests 19 and 34 are presented in Appendix~\ref{sec:handline_figs}.

@@

\appendix
\chapter{Appendix}
\label{chap:appendix}

\section{Additional Figures}
\label{sec:additional_figs}

\subsection{Monitor Figures}
\label{sec:monitor_figs}

@@

\subsection{Handline Figures}
\label{sec:handline_figs}

>>>>

Fig.~\ref{fig:Test_16_BDP_A10_Avg_All} contains a plot of the average measured velocity through the interior stairwell door (A10) for the straight, narrow fog, and wide fog stream patterns during Test 16. Similar plots of the average measured velocity through the interior doorway for Tests 17, 33, and 70 are presented in Appendix~\ref{chap:monitor_plots}.

@@

Fig.~\ref{fig:Test_18_BDP_A10_Avg_All} contains a plot of the average measured velocity through the interior stairwell door (A10) for the straight, narrow fog, and wide fog stream patterns being applied in a fixed position, a sweeping pattern, a clockwise rotation, and counter clockwise rotation during Test 18. Similar plots of the average measured velocity through the interior doorway for Tests 19 and 34 are presented in Appendix~\ref{chap:handline_plots}.

@@

\appendix
\chapter{Monitor Test Plots}
\label{chap:monitor_plots}

@@

\chapter{Handline Test Plots}
\label{chap:handline_plots}
